```{r init, message=FALSE}
require(ggplot2)
require(plyr)
require(Hmisc)
require(reshape)
require(grid)

source('meta.R')
source('multiplot.R')
source('figs.R')
```

Figure 0
--------

Randomly selected examples of simulated reinforcement learning, including expected _value_, the reward prediction error _rpe_, along with the probabiity of receiving a reward, _p_. The top panel features examples from the maximum liklihood fitting procedure. The bottom two panels demonstrate show how _rpe_ (middle) and _value_ (bottom) learning changes are a function of the learning rate. Each column in the bottom two panels matches a value of alpha, ranging from 0.1 to 0.9 in 0.2 steps. All example data is from the _learn_ behavoiral models.  _Random_ timecourse showed similar overall behavoir, without the consistent upward (or downward) trend indicative of learning.


```{r f0, eval=FALSE}
# Get data, fit then 
# gather set together.

numtraces <- 5

b.fit <- read.table('../data/behave_rwfit100_l.csv', sep=',', header=TRUE)
b.fit.r <- read.table('../data/behave_rwfit100_r.csv', sep=',', header=TRUE)

alphas <- c('01', '03', '05', '07', '09')
b.set <- NULL
for(alpha in alphas){
  df <- read.table(paste(
    '../data/behave_rwset100_l_', alpha, '.csv', sep=""), 
    sep=',', header=TRUE)
  df$alpha <- as.factor(rep(alpha, nrow(df)))
  b.set <- rbind(b.set, df)
}

str(b.fit)
str(b.fit.r)
str(b.set)

# Reshape for ggplot2
b.fit <- melt(b.fit, id=c("count","index"))
colnames(b.fit) <- c("iter", "index", "variable", "value")

b.fit.r <- melt(b.fit.r, id=c("count","index"))
colnames(b.fit.r) <- c("iter", "index", "variable", "value")

b.set <- melt(b.set, id=c("alpha", "count", "index"))
colnames(b.set) <- c("alpha", "iter", "index", "variable", "value")

str(b.fit)
str(b.fit.r)
str(b.set)

# Fit
# Make a big matrix of time courses
# Rows are repeats, cols are kinds
toplot <- (b.fit$variable=="rpe") | (b.fit$variable=="value") | (b.fit$variable=="p") | (b.fit$variable=="acc")

# rename facets
b.fit$variable <- revalue(b.fit$variable, c("rpe"="RPE", "p"="Pr"))

toplot <- toplot & (b.fit$iter < numtraces)
f0.p1 <- ggplot(droplevels(b.fit[toplot,]), aes(x=index, y=value)) +
  geom_line() +
  facet_grid(iter~variable) +
  xlab("") + ylab("") + ggtitle("A") + 
  theme(
      legend.key.size = unit(.3, "cm"),
      #legend.position = lp,
      plot.background = element_blank(),   ## Main facet bkg
      panel.grid.major = element_blank(),  ## Major grid lines
      panel.grid.minor = element_blank(),  ## Minor grid lines
      panel.border = element_blank(),      ## Facet border
      panel.background = element_blank(),  ## Facet bkg
      panel.margin = unit(.5, "lines"),
      panel.margin = unit(1.7, "lines"),
      axis.text.y=element_blank(),       ## y lab
      axis.ticks.y=element_blank(),      ## y ticks
      strip.text.y = element_blank(),
      #strip.text.y = element_text(angle=0),## facet name rotate
      strip.background = element_blank()   ## Fam1e bckgrnd (grey+box)
    )
print(f0.p1)

# random
toplot <- (b.fit.r$variable=="rpe") | (b.fit.r$variable=="value") | (b.fit.r$variable=="p") | (b.fit.r$variable=="acc")

# rename facets
b.fit.r$variable <- revalue(b.fit.r$variable, c("rpe"="RPE", "p"="Pr"))

toplot <- toplot & (b.fit.r$iter < numtraces)
f0.p1b <- ggplot(droplevels(b.fit.r[toplot,]), aes(x=index, y=value)) +
  geom_line() +
  facet_grid(iter~variable) +
  xlab("") + ylab("") + ggtitle("B") + 
  theme(
      legend.key.size = unit(.3, "cm"),
      #legend.position = lp,
      plot.background = element_blank(),   ## Main facet bkg
      panel.grid.major = element_blank(),  ## Major grid lines
      panel.grid.minor = element_blank(),  ## Minor grid lines
      panel.border = element_blank(),      ## Facet border
      panel.background = element_blank(),  ## Facet bkg
      panel.margin = unit(.5, "lines"),
      panel.margin = unit(1.7, "lines"),
      axis.text.y=element_blank(),       ## y lab
      axis.ticks.y=element_blank(),      ## y ticks
      strip.text.y = element_blank(),
      #strip.text.y = element_text(angle=0),## facet name rotate
      strip.background = element_blank()   ## Fam1e bckgrnd (grey+box)
    )
print(f0.p1b)

# Set
# This matrix is for rpe only,
# cols are alphas

# rename facets
b.set$variable <- revalue(b.set$variable, c("rpe"="RPE", "p"="Pr"))
b.set$alpha <- revalue(b.set$alpha, c("01"="0.1", "03"="0.3", "05"="0.5", "07"="0.7", "09"="0.9"))

toplot <- (b.set$variable=="RPE")
toplot <- toplot & (b.set$iter < numtraces)
f0.p2 <- ggplot(droplevels(b.set[toplot,]), aes(x=index, y=value)) +
  geom_line() +
  facet_grid(iter~alpha) +
  xlab("") + ylab("") + ggtitle("C") + 
  theme(
      #legend.key.size = unit(.3, "cm"),
      #legend.position = lp,
      plot.background = element_blank(),   ## Main facet bkg
      panel.grid.major = element_blank(),  ## Major grid lines
      panel.grid.minor = element_blank(),  ## Minor grid lines
      panel.border = element_blank(),      ## Facet border
      panel.background = element_blank(),  ## Facet bkg
      panel.margin = unit(.5, "lines"),
      #panel.margin = unit(1.7, "lines"),
      axis.text.y=element_blank(),       ## y lab
      axis.ticks.y=element_blank(),      ## y ticks
      strip.text.y = element_blank(),
      #strip.text.y = element_text(angle=0),## facet name rotate
      strip.background = element_blank()   ## Fam1e bckgrnd (grey+box)
    )
print(f0.p2)

# This matrix is for value only,
# cols are alphas
toplot <- (b.set$variable=="value")
toplot <- toplot & (b.set$iter < numtraces)
f0.p3 <- ggplot(droplevels(b.set[toplot,]), aes(x=index, y=value)) +
  geom_line() +
  facet_grid(iter~alpha) +
  xlab("Trial") + ylab("") + ggtitle("D") + 
  theme(
      #legend.key.size = unit(.3, "cm"),
      #legend.position = lp,
      plot.background = element_blank(),   ## Main facet bkg
      panel.grid.major = element_blank(),  ## Major grid lines
      panel.grid.minor = element_blank(),  ## Minor grid lines
      panel.border = element_blank(),      ## Facet border
      panel.background = element_blank(),  ## Facet bkg
      panel.margin = unit(.5, "lines"),
      #panel.margin = unit(1.7, "lines"),
      axis.text.y=element_blank(),       ## y lab
      axis.ticks.y=element_blank(),      ## y ticks  
      strip.text.y = element_blank(),
      #strip.text.y = element_text(angle=0),## facet name rotate
      strip.background = element_blank()   ## Fam1e bckgrnd (grey+box)
    )
print(f0.p3)

# Combine them into one pdf, making the figure
pdf("figs/f0_behave.pdf", width=6, height=9)
multiplot(f0.p1, f0.p1b, f0.p2, f0.p3, cols=1)
dev.off()
```

Figure 1
--------

Distribution of *t*-values for all _confusion_ experiments, which examined the precision of model-based fMRI between related, but theoretically distinct, trial-level predictors. The five predictors were acc (red), p (yellow), rand (green), rpe (blue), and value (violet). In the left facet column is _random_ behavoir models, on the right is the _learn_ing behavoir.  Each row is repeat of the same 5 predictors (fill colors) for a differnt BOLD signal (see row labels on the right).  That is, each predictor (with noise added) took a turn as the BOLD signal.  Panel **A** represents the model only approach while **B** represents the box and model approach - the recommended procedure for model-based fMRI (TOD).

Probability density estimates of conjunction *t*-statistics for _confusion_ simulations.  Significance thresholds at both `p < 0.05` and `p < 0.0001` are shown in orange and red, respectivily,

Figure 2
--------

Percent significance  ...

```{r f1andf2, eval=TRUE, cache=FALSE}
# Fetch data, learn and random sets
learn <- read.table('../stats/rwfit1000_l_params_tvalue_conj.csv',sep=",",header=TRUE)
learn <- cbind(learn$value, learn$p, seperate_meta(as.character(learn$path)))
colnames(learn) <- c("t","p", "iter", "bold", "model", "design")
learn <- droplevels(learn[learn$bold != 'box',])
learn$exp <- rep("learn", nrow(learn))

random <- read.table('../stats/rwfit1000_r_params_tvalue_conj.csv',sep=",",header=TRUE)
random <- cbind(random$value, random$p, seperate_meta(as.character(random$path)))
colnames(random) <- c("t","p", "iter", "bold", "model", "design")
random <- droplevels(random[random$bold != 'box',])
random$exp <- rep("guess", nrow(random))

# Join the sets
both <- rbind(learn, random)
levels(both$model) <- c("acc", "box_acc", "box_p", "box_rand", 
                        "box_rpe", "box_value", "p", "rand", 
                        "rpe", "value")

# Create and join sig
learnsig <- f1.f2.sigfac(learn)
learnsig$exp <- rep("learn", nrow(learnsig))
randomsig <- f1.f2.sigfac(random)
randomsig$exp <- rep("guess", nrow(randomsig))

bothsig <- rbind(learnsig, randomsig)
bothsig$mean <- bothsig$mean*100  ## Make into percent
levels(bothsig$model) <- c("acc", "box_acc", "box_p", "box_rand", 
                           "box_rpe", "box_value", "p", "rand", 
                           "rpe", "value")

# Get mean frac sig, dropping bold/mode match
dropmatch <- NULL
for(i in nrow(bothsig)) {
  m <- grep(bothsig$bold[i], grep(bothsig$model[i]))
  if(m > 0){
    dropmatch <- c(dropmatch, TRUE)
  } else {
    dropmatch <- c(dropmatch, FALSE)
  }
  print(dropmatch)
  print(mean(bothsig$mean[dropmatch]))
}


# Rename things
both$bold <- revalue(both$bold, c("rpe"="RPE", "p"="Pr"))
both$model <- revalue(both$model, c("box_acc"="acc", "box_rpe"="RPE",
                                    "box_value"="value", "box_p"="Pr",
                                    "box_rand"="rand", 
                                    "rpe"="RPE", "p"="Pr"))
both$bold <- factor(both$bold, levels=c("acc", "Pr", "RPE", "value", "rand"))
both$model <- factor(both$model, levels=c("acc", "Pr", "RPE", "value", "rand"))

# sig counts
bothsig$bold <- revalue(bothsig$bold, c("rpe"="RPE", "p"="Pr"))
bothsig$model <- revalue(bothsig$model, c("box_acc"="acc", "box_rpe"="RPE",
                                    "box_value"="value", "box_p"="Pr",
                                    "box_rand"="rand", 
                                    "rpe"="RPE", "p"="Pr"))
bothsig$bold <- factor(bothsig$bold, levels=c("acc", "Pr", "RPE", "value", "rand"))
bothsig$model <- factor(bothsig$model, levels=c("acc", "Pr", "RPE", "value", "rand"))

# Fig 1
f1.p1 <- f1.f2.pdist(both[both$design == "Model",], "bottom") + ggtitle("A")
f1.p2 <- f1.f2.sigpoints(bothsig[bothsig$design == "Model",]) + ggtitle("A")
print(f1.p1)
print(f1.p2)

# pdf(file="figs/model.pdf", width=5, height=8.5)
# multiplot(f1.p1, f1.p2, cols=1)
# dev.off()

# Fig 2
f2.p1 <- f1.f2.pdist(both[both$design == "Box_and_model",], "bottom") + ggtitle("B")
f2.p2 <- f1.f2.sigpoints(bothsig[bothsig$design == "Box_and_model",]) + ggtitle("B")
print(f2.p1)
print(f2.p2)

# pdf(file="figs/box_and_model.pdf", width=5, height=8.5)
# multiplot(f2.p1, f2.p2, cols=1)
# dev.off()
# 
# pdf(file="figs/all_set.pdf", width=8, height=8.5)
# multiplot(f1.p1, f1.p2, f2.p1, f2.p2, cols=2)
# dev.off()

pdf(file="figs/f1_p1.pdf", width=5, height=9)
multiplot(f1.p1, f2.p1, cols=1)
dev.off()

pdf(file="figs/f2_p2.pdf", width=5, height=9)
multiplot(f1.p2, f2.p2, cols=1)
dev.off()
```
    
Figure 3
-------

The 'parameter selection' simulations. _Top_: probability density estimates for all possible of BOLD and model-based predictor sets. _Bottom_: Percent significant at both `p < 0.05` and `p < 0.0001` levels (in orange and red, respectivily).


```{r f3, eval=FALSE}
# Get data and give cols better names
set <- read.table('../stats/rwset1000_l_params_tvalue_conj.csv',sep=",",header=TRUE)
set <- cbind(set$value, set$p, seperate_meta_set(as.character(set$path)))
colnames(set)
colnames(set) <- c("t", "p", "iter", "bold", "bold_alpha", "model", "model_alpha", "design")
str(set)

# Select data
set <- droplevels(set[set$bold != 'Model',])
str(set)

# --
# Figure 3 p1 and 2, density
tmps.r <- set[set$bold == 'rpe',]
tmps.r <- tmps.r[grep('rpe', tmps.r$model),]
str(tmps.r)

tmps.v <- set[set$bold == 'value',]
tmps.v <- tmps.v[grep('value', tmps.v$model),]
str(tmps.v)

tmps.c <- droplevels(rbind(tmps.r, tmps.v))
str(tmps.c)

setsig <- f3.sigfac(tmps.c)
setsig$mean <- setsig$mean * 100  ## into percent
str(setsig)

# Rename
tmps.c$bold <- revalue(tmps.c$bold, c("rpe"="RPE"))
setsig$bold <- revalue(setsig$bold, c("rpe"="RPE"))

f3.p1 <- f3.pdist(tmps.c, "bottom") + ggtitle("A"); print(f3.p1) 
f3.p2 <- f3.sigpoints(setsig) + ggtitle("B"); print(f3.p2)

# Compose plots into the figure
pdf(file="figs/f3_set.pdf", width=7.25, height=5.5)
multiplot(f3.p1, f3.p2, cols=1)
dev.off()

# p1 rpe
# tmps <- set[(set$bold == 'rpe'),]
# tmps <- tmps[grep('rpe', tmps$model),]
# str(tmps)
# setsig.rpe <- f3.sigfac(tmps)
# setsig.rpe$mean <- setsig.rpe$mean * 100  ## into percent
# str(setsig.rpe)
# 
# f3.p1 <- f3.pdist(tmps, "right"); print(f3.p1)
# f3.p3 <- f3.sigpoints(setsig.rpe); print(f3.p3)
# 
# # p2 value
# tmps <- set[(set$bold == 'value'),]
# tmps <- tmps[grep('value', tmps$model),]
# setsig.val <- f3.sigfac(tmps)
# setsig.val$mean <- setsig.val$mean * 100  ## into percent
# 
# f3.p2 <- f3.pdist(tmps, "right"); print(f3.p2)
# f3.p4 <- f3.sigpoints(setsig.val); print(f3.p4)
``` 

Figure 4
--------

Comparison of RL data before and after HRF convolution.

```{r fig4, eval=FALSE}
# Get the data, add an exp code for faceting, and reshape
nohrf <- read.table('../data/behave_rwfit100_l.csv',sep=",",header=TRUE)
nohrf$exp <- as.factor(rep("Before HRF", nrow(nohrf)))
hrf <- read.table('../data/behave_rwfit100_l_hrf.csv',sep=",",header=TRUE)
hrf$exp <- as.factor(rep("After HRF", nrow(hrf)))

both <- rbind(nohrf, hrf)                         ## join hrf and nohrf
both <- melt(both, id=c("count","index","exp"))   ## reshape
str(both)
print(unique(both$variable))

# Filter for plotting
both <- both[both$value != 0,]                    ## Drop null trials (numerically not ideal)
mask <- (both$variable == "rpe") | (both$variable == "value") | (both$variable == "p") | (both$variable == "acc")

# rename facets
both$variable <- revalue(both$variable, c("rpe"="RPE", "p"="Pr"))

# Plot
f4.p1 <- ggplot(data=both[mask,], aes(x=value, fill=variable)) + 
    geom_density(alpha=.4, color="black") + 
    # Match colors in fig 1 and 2
    scale_fill_manual(values=c("#F8766D", "#A3A500", "#00BF7D", "#00B0F6"),
                      name = "Predictor") +
    facet_grid(.~exp) + 
    ylab("Density (AU)") +
    xlab("y") +
    theme_bw() +
    #coord_cartesian(ylim=c(0,3)) +
    theme(
      legend.key.size = unit(.3, "cm"),
      legend.position = "bottom",
      #plot.background = element_blank(),   ## Main facet bkg
      panel.grid.major = element_blank(),  ## Major grid lines
      panel.grid.minor = element_blank(),  ## Minor grid lines
      #panel.border = element_blank(),      ## Facet border
      panel.background = element_blank(),   ## Facet bkg
      panel.margin = unit(.5, "lines"),
      #panel.margin = unit(1.7, "lines"),
      #axis.text.y=element_blank(),       ## y lab
      #axis.ticks.y=element_blank(),      ## y ticks  
      strip.text.y = element_text(angle=0),## facet name rotate
      strip.background = element_blank()   ## Fam1e bckgrnd (grey+box)
    )
print(f4.p1)
ggsave("figs/f4_hrf_effect.pdf", plot=f4.p1, width=4, height=2.5)
```